High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-11 conclusion.tex
Award Number.

{\bf \footnotesize This work is funded by DOE XXXXXX \par}

>>>>

{\bf \footnotesize Acknowledgements: This work is funded by Award number DE-
SC0016280 from the Office of Advanced Scientific Computing Research within the
Department of Energy. This research used resources of the Oak Ridge Leadership
Computing Facility at the Oak Ridge National Laboratory, which is supported by
the Office of Science of the U.S.Department of Energy under Contract No. DE-
AC05-00OR22725. \par}
